Reasoning About a Machine with Local Capabilities

### 2018-05-03 toplas/paper.tex
Suggestion for macro section. Should we say something about temporary registers?
Added later definition for cofes to toplas appendix
Added text about malloc implementation

% Uncomment me to disable comments
\renewcommand\lau[1]{}
\renewcommand\dominique[1]{}
\renewcommand\lars[1]{}

@@

\itoplassug{Add the assumption that the malloc capability in examples
  satisfies specification.}

\subsection{Reusable macro instructions}
\label{subsec:macros}
%\itoplassug{Add examples of macros to this section to make it clear what we mean by macros.\\}
%\itoplassug{Reviewer C, ESOP, asks for high-level specifications for the macros in the style of malloc. I am not sure we want to actually include this in the submission, so it is maybe not here we should put our attention. (see review in tex comment)\\}
% Finally, as already mentioned above, the approach relies on `call` and `scall` macro-instructions that are only outlined in the submission, and described by very complicated pseudocode and English prose in the companion technical appendix.  I still miss a fully formal description of 1- what instructions the macros expand to, exactly, and 2- what contract they satisfy (in the style of the contract for malloc in section 2 of the technical appendix).
We define a number of reusable macros capturing the calling convention as well
as other conveniences. The macros that utilise the stack assume that it is
available in register $r_\stk$.

@@

>>>>

% Uncomment me to disable comments
%\renewcommand\lau[1]{}
%\renewcommand\dominique[1]{}
%\renewcommand\lars[1]{}

@@

\subsection{Reusable macro instructions}
\label{subsec:macros}
The focus of this work is not to give a definitive specification and
implementation of malloc which is why we do give a malloc implementation. We
are, however, confident that it is possible to make an implementation of malloc
that satisfies the malloc specification in Definition~\ref{spec:malloc}. There
are in particular two simplifications in our system that makes things easy:
First, we do not consider deallocation of memory which means that the data
structure malloc uses to keep track of free memory does not have to handle
reclaimed memory. Second, the malloc specification does nor permit malloc to run
out of memory and thus prevent allocation. This is possible on our simple
capability machine because it has an infinite address space. The capability with
an infinite range of authority would of course need to be part of malloc, but it
could also double as the data structure that keeps track of free memory.
\itoplassug{If we have references for malloc being difficult, we could add that
  to the text.}
%\itoplassug{Add the assumption that the malloc capability in examples
%  satisfies specification.}

%\itoplassug{Add examples of macros to this section to make it clear what we mean by macros.\\}
%\itoplassug{Reviewer C, ESOP, asks for high-level specifications for the macros in the style of malloc. I am not sure we want to actually include this in the submission, so it is maybe not here we should put our attention. (see review in tex comment)\\}
% Finally, as already mentioned above, the approach relies on `call` and `scall` macro-instructions that are only outlined in the submission, and described by very complicated pseudocode and English prose in the companion technical appendix.  I still miss a fully formal description of 1- what instructions the macros expand to, exactly, and 2- what contract they satisfy (in the style of the contract for malloc in section 2 of the technical appendix).
We define a number of reusable macros capturing the calling convention as well
as other conveniences. The macros that utilise the stack assume that it is
available in register $r_\stk$.
\itoplassug{Lau, suggestion: should we mention temporary registers? They are
  used in the macros, but it seems like a minor technical detail.}

@@

\begin{definition}[Later on c.o.f.e.'s]
  Let $\left( X, \left( \nequal \right)_{n=0}^{\infty}\right)$ be a \cofe{}. Define
  \[
  \blater \left( X, \left( \nequal \right)_{n=0}^{\infty}\right) = \left( X, \left(\nequal' \right)_{n=0}^{\infty}\right)
  \] 
  where for all $x$ and $x'$ in $X$
  \[
  x \nequal' x'\textit{  iff  } \begin{cases}
    \top              & \text{if } n=0 \\
    x \nequal[n-1] x' & \text{if } n > 0
  \end{cases}
  \]
%  The set in the \cofe{} remains the same, but the equality relation is ``moved'' so it is equal at an earlier time. \todo[inline]{can we here say that to look under a later we have to use a computation step?}
\end{definition}
